\documentclass[letterpaper]{deedy-resume-openfont} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Linda}{Zheng}{ % Your name
\href{mailto:lindazheng1993@gmail.com}{lindazheng1993@gmail.com | 469-305-9242 | yaylinda.github.io/my-website-vue-v2} % Your contacv information
}

%----------------------------------------------------------------------------------------
% LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.29\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Rice University}

\descript{Bachelor of Science in Computer Science, Statistics}
\location{Aug 2012 - May 2016 \\ GPA: 3.7}

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Computer Science}
\textbullet{} Artificial Intelligence\\
\textbullet{} Game Creation \& Design\\
\textbullet{} Operating Systems\\
\textbullet{} Concurrent Programming\\
\textbullet{} Database Systems and Design\\
\textbullet{} Object Oriented Programming\\
\textbullet{} Compilers\\
\textbullet{} Data Structures\\
\textbullet{} Advanced Algorithms\\

\sectionsep % Some whitespace after the section

\subsection{Statistics}
\textbullet{} Data Mining\\
\textbullet{} Statistical Learning\\
\textbullet{} Financial Time Series\\
\textbullet{} Regression Analysis\\
\textbullet{} Bioinformatics\\

\sectionsep % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\textbullet{} Java\\
\textbullet{} Python\\
\textbullet{} JavaScript/Typescript\\
\textbullet{} HTML/CSS\\
\textbullet{} SQL\\
\textbullet{} R\\
\textbullet{} Matlab\\
\textbullet{} C\\
\textbullet{} C++

\sectionsep % Some whitespace after the section

\subsection{Frameworks}
\textbullet{} AWS\\
\textbullet{} Spring/SpringBoot\\
\textbullet{} Vue\\
\textbullet{} Angular\\
\textbullet{} React\\
\textbullet{} Android\\
\textbullet{} iOS\\

\sectionsep % Some whitespace after the section

\subsection{Github}
\textbullet{} https://github.com/yaylinda

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
% RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.7\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Redfin}
\descript{| Software Development Engineer II}

\location{Jan 2020 - Present | Frisco, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Full-stack engineer on the Home Services team. Working with Java SpringBoot Microservices to develop RESTful API's, Kubernetes for Cloud Container deployment, Netflix Conductor for Microservice Orchestration, React for frontend development. 
\end{tightemize}

\sectionsep % Some whitespace after the section


\runsubsection{Capital One}
\descript{| Senior Software Engineer}

\location{July 2019 - Jan 2020 | Plano, TX}

\begin{tightemize}
\item Designed and and developed Metadata Management Service. Designed system to discover metadata across entire corporation and with automated data pipeline to bring the data into team's internal database to be used for the marketing platform. Developed frontend application with various user roles to facilitate the data onboarding process. (Java, SpringBoot, Vue, PostgreSQL, MemSQL, AWS, ECS)
\item Patent pending on dataset collation process to use data from multiple sources, with multiple cadences as consolidated dynamic view. (Java, SpringBoot, NodeJS, SQL)
\item Continued maintenance and development on six microservices for marketing platform. (Java, SpringBoot, NodeJS, SQL)
\item Demonstrated leadership by mentoring new team member on Vue development, and leading sub-team with detailed requirements and dates.
\end{tightemize}

\sectionsep % Some whitespace after the section

\runsubsection{Capital One}
\descript{| Software Engineer}
\location{July 2017 - July 2019 | Plano, TX}

\begin{tightemize}
\item Designed and developed an enterprise-wide platform for automated, real-time, always-on, intelligent marketing platform. Primary developer and owner of six microservices, and one of three frontend developers. (Java, SpringBoot, NodeJS, MemSQL, PostgreSQL, Javascript/Typescript, HTML/CSS, WebComponents, AWS)
\item Developed an Ad Server integrated with Google AdSense to serve dynamically rendered, individually customized vehicle ads based on customer information. Intelligently parses vehicle make, model, and body type from source website to serve context-aware within the user's area. API responds within 50ms per call. Patent pending. (Java, SpringBoot, NodeJS, ECS, Redis, HTML/CSS, Mustache)
\item Instrumented application metrics for over a dozen microservices, using Prometheus. Authored rules for PagerDuty alerts based on metrics, with Slack integration. (Prometheus, PromQL, Slack) 
\item Implemented API and UI for Call Center agents to capture notes from customer communications. (Java, Angular, AWS, PostgreSQL)
\item Designed and implemented Automated Handwriting System using RNN Machine Learning Algorithms, with UI, server, and polling client to write greeting cards to customers. (Python, Tensorflow, Angular, AxiDraw V3)
\item Developed enterprise-wide API for Cloud file storage abstraction, and an automated data migration system to extract files from the on-premise Data Center to the Cloud with unique IDs for fast retrieval. (Java, ECS, S3, SQS, CFT, SQL)
\end{tightemize}

\sectionsep % Some whitespace after the section

\runsubsection{Capital One}
\descript{| Associate Software Engineer}
\location{July 2016 - July 2017 | Plano, TX}

\begin{tightemize}
\item Developed an Angular Widget for all Financial Services applications to capture customer feedback. (Java, SpringBoot, Angular, AWS, PostgreSQL, Splunk)
\item Built ad-hoc data analysis platform using open-source Apache Zeppelin. Implemented features: connection to Redshift Clusters, schema browser, SQL parser/linter/visualizer. (Java, Angular, AWS, Redshift, ElasticSearch, Spark, R, Python)
\end{tightemize}

\sectionsep % Some whitespace after the section

%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
% SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

\begin{minipage}[t]{0.29\textwidth} % The left column takes up 33% of the text width of the page

\section{}

\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.7\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Internships}

\runsubsection{Shape Security}
\descript{| KPCB Fellow + Software Engineering Intern}
\location{May 2015 - Aug 2015 | Mountain View, CA}

One of 60 out of 2500+ applicants chosen to be a Kleiner, Perkins, Caufield and Byers Engineering Fellow of 2015. Interned at Shape Security, one of KPCB's portfolio companies. There, I upgraded Shape Security's open-source project, to support tooling for ECMAScript 6, which was just coming out at the time. Tools include: Abstract Syntax Tree node generator, Parser, Code Generator from AST, AST Validator, Fuzzer, Reducer, (De)Serializer. So I could write Java to generate JavaScript code! At the end of the summer, I presented my experience at the South Bay JavaScript Meetup, hosted by Shape Security. 

\sectionsep % Some whitespace after the section

%------------------------------------------------

\runsubsection{PROS}
\descript{| Software Engineering Intern}

\location{May 2014 - Aug 2014 | Houston, TX}
Worked on three distinct projects during my internship:
Project \#1 - Implemented ElasticSearch, LogStash, Kibana stack for various application logs. (ELK)
Project \#2 - Built nightly task that summarizes flight booking statistics and sends analytics email, using map-reduce algorithms. (Java, Cassandra)
Project \#3 - Created APIs for Notification and Notes Services for a Travel Agent System. (Java)

\sectionsep % Some whitespace after the section

%------------------------------------------------

\runsubsection{Jones McClure Publishing}
\descript{| Software Engineering Intern}

\location{June 2013 - Sep 2013 | Houston, TX}
Built two dynamic web applications and mobile-compatible versions: Income Tax Calculator, Child Support Calculator. (C\#, Javascript/HTML/CSS). Also built an Administration site to track and display internal business data. (C\#, Javascript/HTML/CSS).


\sectionsep % Some whitespace after the section

%------------------------------------------------
% Other projects
%------------------------------------------------

\section{Other Projects}

%------------------------------------------------

\runsubsection{Simple War}
\descript{| Personal Project}

\location{2018-Present | Anywhere}
REST-ful, turn-based game with online match-making. Front-end built in Angular 4, with Java as the API and game-engine layer, MongoDB for game data storage, and websockets for real-time game-board updates. Players take turns placing cards (troops, walls, special) on the board. Player wins when a certain number of points have been scored. Points are earned from successfully moving troops across the board to the opponent's side, while the opponent places cards to stop advancement. \href{http://3.85.160.165:4200/}{Give it a try (looks better in half-screen)}.

\sectionsep % Some whitespace after the section

%------------------------------------------------
\runsubsection{Parking Navigator}
\descript{| Company Hackathon}

\location{Aug 2017 | Plano, TX}
Project for internal Hackathon hosted by Capital One. Drone flies around campus on a pre-set path, taking aerial shots of parking lot. Sends pictures to server for processing, using edge detection to find empty parking spots. 

\sectionsep % Some whitespace after the section

%------------------------------------------------

\runsubsection{Decoding the Brain from Electrocorticographical Readings}
\descript{| Undergraduate Senior Thesis in Statistics}

\location{Jan 2016 - May 2016 | Houston, TX}
Analyzed ECoG data of brain frequencies obtained from 42 nodes placed on the brain of an epileptic patient while the patient watched videos of a person saying "rock" or "rain" with blurry or clear visual and audio. Goal was to be able to classify the type of stimuli based on the brain frequencies data. Used 3D and 4D Higher Order Partial Least Squares Methods for analysis. Found strong effects of priming in the brain (audio section of the brain became activated when visual start even if there is no audio yet, and vice-versa).

\sectionsep % Some whitespace after the section

%------------------------------------------------

\runsubsection{Computer Game Creation}
\descript{| Senior Project}

\location{Jan 2015 - May 2015 | Houston, TX}
Multi-player, cross-platform game, combining the game-play mechanics of Doodle Jump, and competitive nature of Mario Kart. The game is called \href{http://poporopo.nimbusmog.com}{"Poporopo"} (looks better in half-screen).

\sectionsep % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}